FIXME

### 2013-08-28 writeups/proposal/proposal.tex
foo
Former-commit-id: 3c53327b0c4a2563025003c51db18c07c3d89a52 [formerly bc7cd4c8412fc5562d212c56fc79b75fdeac0b87]
Former-commit-id: 9b5a12674b249c6284fb576bbb3102a8c62dfb7f

\title{Psyc 601 Multivariate Statistics Project}
\shorttitle{Psyc 601 Project}

@@

\abstract{
  The base StackOverflow tag-prediction model from the Fall '12 Psychometrics course was improved by incorporating the words in the body of the post and the post author's specific tagging history.
  We focused on hashtag creation as a specific human behavior, since understanding and modeling hashtag creation can lead to improved human-computer systems that can better identify users' goals and interests.
  We used multivariate logistic regression statistical techniques to guide the model building process, and found that adding the two model terms improved model accuracy from 56\% to 69\%.
  The model is a successful case showing that ACT-R's declarative memory retrieval equations scale, and are relevant to task domains that require large-scale knowledge stores.
}

\keywords{StackOverflow, Machine Learning, ACT-R, Tagging, Large-Scale Semantic Memory}

>>>>

\title{FIXME}
\shorttitle{}

@@

\abstract{
  FIXME
}

\keywords{FIXME}
